\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2015-09-21 overview.tex
Edits

\begin{enumerate}
\item The real components of a distributed system must be wrapped inside \psharp machines. In addition, the environment of the system must be modeled using \psharp, so all external nondeterminism can be captured. We collectively refer to the environment model of a system and its wrapped components as the \psharp \emph{test harness}. This test harness can be used by \psharp to drive the system towards interesting behaviors.

@@

\item All the asynchrony due to message passing in the system must be modeled using the \psharp event-sending APIs. Likewise, all other sources of nondeterminism, such as failures and timer expiration, must be modeled using appropriate \psharp APIs. This step allows \psharp to systematically explore all asynchronous event handler interleavings and all other sources of nondeterminism during testing (see \S\ref{sec:psharp:testing}).
\end{enumerate}

\noindent
\psharp uses modern object-oriented language features such as \emph{interfaces} and \emph{virtual method dispatch} to connect the real code with the modeled code. Programmers in industry are used to working with such features, and heavily use them in production for testing purposes. In our experience, this significantly lowers the bar for product teams inside Microsoft to embrace \psharp for testing.

>>>>

\begin{enumerate}
\item The real components of a distributed system must be wrapped inside \psharp machines. In addition, all the asynchrony due to message passing in the system must be modeled using the \psharp event-sending APIs.

\item The environment of the system must be modeled using \psharp. \psharp offers APIs for obtaining non-deterministically chosen values, which can be used to simulate failures, timers, etc. (see \S\ref{sec:method:driver}). This step captures external sources of nondeterminism. \psharp's testing engine can then systematically explore all choices, enumerating different asynchronous event interleavings, possible points of failures, timers firing, etc. (see \S\ref{sec:psharp:testing}).

@@

%\item Likewise, all other sources of nondeterminism, such as failures and timer expiration, must be modeled using appropriate \psharp APIs. This step allows \psharp to systematically explore all asynchronous event handler interleavings and all other sources of nondeterminism during testing (see \S\ref{sec:psharp:testing}).
\end{enumerate}

\noindent
We collectively refer to the environment model of a system and its wrapped components as the \psharp \emph{test harness}. This test harness can be used by \psharp to drive the system towards interesting behaviors.
\psharp uses modern object-oriented language features such as \emph{interfaces} and \emph{virtual method dispatch} to connect the real code with the modeled code. Programmers in industry are used to working with such features, and heavily use them in production for testing purposes. In our experience, this significantly lowers the bar for product teams inside Microsoft to embrace \psharp for testing.

### 2015-09-21 related.tex
Edits

Tools such as CrystalBall~\cite{yabandeh2009crystalball} and \textsc{DeMeter}~\cite{guo2011practical} employ techniques based on dynamic partial order reduction~\cite{lauterburg2010evaluating} to reduce the exploration state-space. The SAMC~\cite{leesatapornwongsa2014samc} model checker offers a way of incorporating application-specific information during systematic testing, but the focus is still on reducing the set of possible interleavings. Although SAMC is orders of magnitude faster than previous testing techniques, the authors mention that their ``extensive evaluation exercised more than 100,000 executions and used approximately 48 full machine days''~\cite{leesatapornwongsa2014samc}. \psharp is able to explore a similar number of iterations in a matter of hours, and find serious bugs in seconds (see \S\ref{sec:eval}). However, we do \emph{not} claim that \psharp is faster; as aforementioned, we focus on compositional testing, whereas prior work typically focuses on testing an entire system. We are just trying to solve a similar problem at a very different level.

>>>>

Tools such as CrystalBall~\cite{yabandeh2009crystalball} and \textsc{DeMeter}~\cite{guo2011practical} employ techniques based on dynamic partial order reduction~\cite{lauterburg2010evaluating} to reduce the exploration state-space. The SAMC~\cite{leesatapornwongsa2014samc} model checker offers a way of incorporating application-specific information during systematic testing to reduce the set of interleavings that they explore. These techniques are complementary to our approach: \psharp's systematic testing engine could use them for reducing the number of iterations it explores, just as the other tools can use language technnology (like \psharp) to write models and reduce the complexity of the system under test.

% Further, note that we operate at a different scale by focusing on compositional testing. For instance, SAMC reports orders of magnitude speedup over previous testing techniques, but executing 100,000 runs still took ``approximately 48 full machine days''~\cite{leesatapornwongsa2014samc}. In our case studies, we execute a similar number of iterations in a matter of hours, and find serious bugs in seconds (see \S\ref{sec:eval}). This does \emph{not} imply that \psharp is faster (nor we attempt to make that claim); but simply that we explore behaviors at a different level.

%as aforementioned, we focus on compositional testing, whereas prior work typically focuses on testing an entire system. %We are just trying to solve a similar problem at a very different level.
